---
title: "linear model from Web"
author: "Alexis Velasco"
date: "Summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS


### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

The data seems to show a positive linear relationship between SIMS and ARM. By the plot points going up shows ARMS increases as SIMS do.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The numerical results are showing a positive correlation, or when the dependent variable and independent get bigger together. 



### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The inferential data shows an adjusted r-squared of 0.467 with a standard error of 1.226. When we fit the model it gave us this equation of SIMS=-4.095+0.054563*ARM for the fit line. 

#### Predict at target point

The value at the target point  is 0.7063836. 

```{r}
pdata<- data.frame(ARM=88,GRIP=94)
```

```{r}
predict(model.1,pdata)
```

#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point()
basicNN + geom_point() + geom_smooth(method=lm)
```
  
  The scatter plot with model.1 is showing the best fit line for the data.

## Model 2 SIM~GRIP


### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

 The scatter plot show the relation between SIMS and GRIP having a positive correlation.
 
### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```
 
 This numerical data shows the positive coloration between SIMS and GRIP. The positive relation between SIMS and ARM is  higher than GRIP and SIMS.
 
### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The inferential data shows an adjusted r-squared of 0.4053 with a standard error of 1.295. When we fit the model it gave us this equation of SIMS=-4.809675+0.045463*GRIP for the fit line.

#### predict model.2 at target point

The value of the target point for model 2 is -0.536153

```{r}
pdata<- data.frame(ARM=88,GRIP=94)
```

```{r}
predict(model.2,pdata)
```

#### now add the model fit to our plot for model.2
 
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
basicNN + geom_point()
basicNN + geom_point() + geom_smooth(method=lm)
```

The scatter plot for model.2 seems to have points spread further out than the scatter plot of model.1.

## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```

Arm and grip give us the highest positive coloration between all the models.
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The inferential data shows an adjusted r-squared of 0.5358 with a standard error of 1.144. When we fit the model it gave us this equation of
lm(formula=SIMS = -5.433872 + 0.037311 * ARM + .024470 *GRIP, data = data).

#### predict model.3 at target point
  
 The value of the target of model 3 is 0.1496476.  

```{r}
pdata<- data.frame(ARM=88,GRIP=94)
```

```{r}
predict(model.3,pdata)
```

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1,model.3)
```
The anova that compares the two models of 1 and 3 tell us that that ARM and GRIP combined is the better model. The P value being so small shows us the tiny possibility of getting these results if there was no difference between the models.

### Model.2 vs Model.3

```{r}
anova(model.2,model.3)
```

ARM combined with GRIP is still the better model even when compared to GRIP alone. the smal p value shows the possibailty of getting these results if ther was no diffrence. 

## Informally compare Model.1 with model.2

```{r}
anova(model.1,model.2)
```

The difference between arm and grip is -25.189. Showing that ARM is better than GRIP when comparing with anova. 
